\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-17 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Correction url
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>
changement texte (encore)

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{We thank the referees, as well as the editor, William Kerr, for insightful comments, which helped to significantly improve the paper. We are grateful to Holger G\"{o}rg, S\'{e}bastien Jean and Vincent Vicard for their critics and suggestions on earlier drafts. The paper has also greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the universities of California-Irvine, Paris-Dauphine, Paris-I and Nancy and the Kiel Institute for the World Economy. Any remaining errors are ours. This paper was partly funded by a university grant from the University of Lille. It features %an online appendix containing additional results, available on the authors' websites and on https://github.com/gdaudin/trade_costs.
}}

@@

One can analytically show that $\beta$ is indeed equal to the share of additive costs in total transport costs. To do so, start from the link between the link between cif, fas prices and transport costs by explicitly decomposing between the ad-valorem and the additive costs as $p = \tau \widetilde{p}+ t$, with $\tau \geq 1$ the ad-valorem cost and $t>0 $ the additive shipping charge per kg transported. We can rewrite the additive cost as a function of the cost per USD shipped $\widetilde{t} \equiv \frac{t}{\widetilde{p}}$, leading to:
\begin{equation}
p = \tau \widetilde{p}+ \widetilde{t}\widetilde{p}  \label{eq:base}
\end{equation}
Starting from Equation (\ref{eq:base}), the elasticity of transport costs to the unit price $\widetilde{p}$ can be shown to be equal to:
\begin{eqnarray}
\frac{\partial TC}{\partial \widetilde{p}} \frac{\tilde{p}}{TC}&=& -\frac{\frac{t}{\tilde{p}}}{\tau -1  +\frac{t}{\tilde{p}}} = -\frac{\widetilde{t}}{\tau-1 +\widetilde{t}} \label{eq:tt2}
\end{eqnarray}

Comparing Equations (\ref{eq:alternative}) and (\ref{eq:tt2}), it is straightforward that the unit price-elasticity of transport costs is also equal to the share of additive costs in total transport costs.

While many in the related literature provide an indirect measure of additive costs by estimating the elasticity of freight charges to the unit price (\citealp{hummels_skiba}, \citealp{Lashkaripour-2017}), thereby relying on Equation (\ref{eq:alternative}), we propose an alternative route. Based on Equation (\ref{eq:base}), we exploit our dataset to obtain explicit measures of both transport costs components $\tau$ and $t$ (or $\widetilde{t}$). From this, we can deduce the price-elasticity of transport costs as the share of additive costs in total transport costs through Equation (\ref{eq:tt2}).

@@

\begin{equation}
\frac{p_{ik}}{\widetilde{p}_{ik}} -1 = \tau_{ik}-1 +\frac{t_{ik}}{ \widetilde{p}_{ik}} \label{eq:base_estimee}
\end{equation}

We follow \cite{Irrazabal_2015} by considering that \textit{i)} both ad-valorem and additive costs are separable between the origin country ($i$) and the product ($k$) dimensions, and \textit{ii)} this separability is in a multiplicative way for the former and an additive way for the latter.
In other words, $\tau_{ik}$ and $t_{ik}$ are written as:\footnote{Notice that, given the magnitude or order of transport costs, assuming an additive or a multiplicative form for country/product fixed effects does not make a substantial difference since, for small values (as we generally obtain), we have $\tau_i\times \tau_k -1\simeq (\tau_i-1) + (\tau_k -1) $ and $t_i+t_k\simeq (1+t_i)\times(1+t_k)-1$.
We also provide a robustness analysis to the separability assumption. Given the much higher number of fixed effects to estimate, we run this robustness check on a sub-sample of goods/origin countries. See Section \ref{sec:robustness} for a detailed presentation of this robustness check.}
\begin{eqnarray}
\tau_{ik} &=& \tau_{i} \times\tau_{k} \label{eq:ad-valorem}\\
t_{ik} &=& t_{i} + t_{k} \label{eq:add}
\end{eqnarray}

@@

The ratio $\frac{p_{ik}}{\widetilde{p}_{ik}}$ has a lower bound of one, since by construction, the import price $p$ cannot be lower than the export price ($p_{ik}\geq\widetilde{p}_{ik}$). Taking into account this constraint in the estimate implies that the error term should be always positive.
We ensure that this constraint is fulfilled by specifying the error term as follows:

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}}-1 =\left(\tau_{i}\times \tau_{k} -1+\frac{t_{i} + t_{k}}{\widetilde{p}_{ik}} \right)\times \exp(\epsilon_{ik})
\end{equation*}
\noindent where $\epsilon_{ik}$ follows a normal law centered on 0.
Considered in logs, the above equation becomes:

@@

>>>>

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{We thank the referees, as well as the editor, William Kerr, for insightful comments, which helped to significantly improve the paper. We are grateful to Holger G\"{o}rg, S\'{e}bastien Jean and Vincent Vicard for their critics and suggestions on earlier drafts. The paper has also greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the universities of California-Irvine, Paris-Dauphine, Paris-I and Nancy and the Kiel Institute for the World Economy. Any remaining errors are ours. This paper was partly funded by a university grant from the University of Lille. It features an online appendix containing additional results, available on the authors' websites and on \url{https://github.com/gdaudin/trade_costs}.}}

@@

One can analytically show that $\beta$ is indeed equal to the share of additive costs in total transport costs. To do so, start from the link between the link between cif, fas prices and transport costs by explicitly decomposing between the ad-valorem and the additive costs as $p = \tau \widetilde{p}+ t$, with $\tau \geq 1$ the ad-valorem cost and $t>0 $ the additive shipping charge per kg transported. We can rewrite the additive cost as a function of the cost per USD shipped $\widetilde{t} \equiv \frac{t}{\widetilde{p}}$, leading to:
\begin{equation}
p = \tau \widetilde{p}+ \widetilde{t}\widetilde{p}  \label{eq:base}
\end{equation}
Starting from Equation (\ref{eq:base}), the elasticity of transport costs to the unit price $\widetilde{p}$ is equal to:
\begin{eqnarray}
\frac{\partial TC}{\partial \widetilde{p}} \frac{\tilde{p}}{TC}&=& -\frac{\frac{t}{\tilde{p}}}{\tau -1  +\frac{t}{\tilde{p}}} = -\frac{\widetilde{t}}{\tau-1 +\widetilde{t}} \label{eq:tt2}
\end{eqnarray}

Comparing Equations (\ref{eq:alternative}) and (\ref{eq:tt2}), it is straightforward that the unit price-elasticity of transport costs (in absolute value, $\beta$) is also equal to the share of additive costs in total transport costs.

While many in the related literature provide an indirect measure of additive costs by estimating the elasticity of freight charges to the unit price (\citealp{hummels_skiba}, \citealp{Lashkaripour_JIE2020}), thereby relying on Equation (\ref{eq:alternative}), we propose an alternative route. Based on Equation (\ref{eq:base}), we exploit our dataset to obtain explicit measures of both transport costs components $\tau$ and $t$ (or $\widetilde{t}$). From this, we can deduce the price-elasticity of transport costs as the share of additive costs in total transport costs through Equation (\ref{eq:tt2}).

@@

\begin{equation}
\frac{p_{ik}}{\widetilde{p}_{ik}} -1 = \tau_{ik}-1 +\frac{t_{ik}}{ \widetilde{p}_{ik}}, ~~\text{with } \tau_{ik}\geq 1 ~\text{and }t_{ik}\geq 0 \label{eq:base_estimee}
\end{equation}

We follow \cite{Irrazabal_2015} by considering that \textit{i)} both ad-valorem and additive costs are separable between the origin country ($i$) and the product ($k$) dimensions, and \textit{ii)} this separability is in a multiplicative way for the former and an additive way for the latter.
In other words, $\tau_{ik}$ and $t_{ik}$ are written as:\footnote{Notice that, given the small magnitude of transport costs, assuming an additive or a multiplicative form for country/product fixed effects does not make a substantial difference since, for small values (as we generally obtain), we have $\tau_i\times \tau_k -1\simeq (\tau_i-1) + (\tau_k -1) $ and $t_i+t_k\simeq (1+t_i)\times(1+t_k)-1$.
We also provide a robustness analysis to the separability assumption. Given the much higher number of fixed effects to estimate, we run this robustness check on a sub-sample of goods/origin countries. See Section \ref{sec:robustness} for a detailed presentation of this robustness check.}
\begin{eqnarray}
\tau_{ik} &=& \tau_{i} \times\tau_{k} \label{eq:ad-valorem}\\
t_{ik} &=& t_{i} + t_{k} \label{eq:add}
\end{eqnarray}

@@

The ratio $\frac{p_{ik}}{\widetilde{p}_{ik}}$ has a lower bound of one, since by construction, the import price cannot be lower than the export price ($p_{ik}\geq\widetilde{p}_{ik}$). Taking into account this constraint in the estimation implies that the error term should be always positive.
We ensure that this constraint is fulfilled by specifying the error term as follows:

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}}-1 =\left(\tau_{i}\times \tau_{k} -1+\frac{t_{i} + t_{k}}{\widetilde{p}_{ik}} \right)\times \exp(\epsilon_{ik})
\end{equation*}
\noindent where $\epsilon_{ik}$ follows a normal law centered on 0. Considering that the LHS is positive by nature, we need to take into account a positivity constraint on the RHS. We fulfill this requirement by taking logs. The above equation then becomes:

@@

\textbf{STOP HERE XXXX }
